Modal type theory based on the intuitionistic epistemic logic

### 2018-01-29 article.tex
added

@@

Proof is similar to \cite{Baren} \cite{Baren2}. We build the following diagram, which commutes by lemmas 5 and 7.

@@

Similar to \cite{Abramsky}, we apply the translation from $\lambda_{{\bf K}}$ to some cartesian closed category with an abritraty applicative functor $\mathcal{K}$, then
we have $[\![\Gamma \vdash M : A]\!] = [x, M [x_i := \pi_i x]]$, so $M =_{\beta \eta} N \Leftrightarrow [\![\Gamma \vdash M : A]\!] = [\![\Gamma \vdash N : A]\!]$

@@

>>>>

  If $M \in SC_A$, where $A$ is a modal-free type, then ${\bf pure \:} M \in SC_{{\bf K}A}$
\end{lemma}

  Induction on the structure of M.
\end{proof}

@@

Proof is similar to \cite{Baren} \cite{Baren2}. We build the following diagram, which commutes by lemmas 8 and 10.

@@

@@

Similar to \cite{Abramsky}, we apply the translation from $\lambda_{{\bf K}}$ to some cartesian closed category with an abritraty applicative functor $\mathcal{K}$, then
we have $[\![\Gamma \vdash M : A]\!] = [x, M [x_i := \pi_i x]]$, so $M =_{\beta \eta} N \Leftrightarrow [\![\Gamma \vdash M : A]\!] = [\![\Gamma \vdash N : A]\!]$.
